MSE Setup

### 2025-04-08 MSEsetup.Rmd
loop_through_fn not working for either case

info <- generate_basic_info(n_stocks = 1, #2,
                            n_regions = 1, #2,
                            n_indices = 1, #2,
                            n_fleets = 1, #2,
                            n_seasons = 4,
                            base.years = year_start:year_end,
                            n_feedback_years = MSE_years,
                            life_history = "long",
                            n_ages = 20,
                            #Fbar_ages = 12,
                            #recruit_model = 2,
                            F_info = list(F.year1 = 0.01, Fhist = "constant", Fmax = 2, Fmin = 0.5, change_time = 0.5, user_F = NULL),
                            catch_info = list(catch_cv = 0.1, catch_Neff = 100),
                            index_info = list(index_cv = 0.1, index_Neff = 100, fracyr_indices = 0.625, q = 0.2),
                            fracyr_spawn = 0.625)

>>>>

info <- generate_basic_info(n_stocks = 1, #2,
                            n_regions = 1, #2,
                            n_indices = 1, #2,
                            n_fleets = 1, #2,
                            n_seasons = 4,
                            base.years = year_start:year_end,
                            n_feedback_years = MSE_years,
                            life_history = "long",
                            n_ages = 20,
                            #Fbar_ages = 12,
                            #recruit_model = 2,
                            F_info = list(F.year1 = 0.01, Fhist = "constant", Fmax = 0.01, Fmin = 0.01, change_time = 0.5, user_F = NULL),
                            catch_info = list(catch_cv = 0.1, catch_Neff = 100),
                            index_info = list(index_cv = 0.1, index_Neff = 100, fracyr_indices = 0.625, q = 0.2),
                            fracyr_spawn = 0.625)
